\documentclass[a4paper, 11pt]{article}
\usepackage{comment} % enables the use of multi-line comments (\ifx \fi) 
\usepackage{fullpage} % changes the margin
\usepackage{hyperref}

\begin{document}
\noindent

\begin{center}
\section*{Retrospective}
\end{center}
\vspace{10 mm}
\section*{Overall}
In our opinion this obligatory assignment has gone by without any significant turbulence. 

\noindent
Collectively we felt rewarded from the work we had put in from the last iteration, meaning that the workload for this iteration was very manageble.


\section*{Challenges:}
\begin{itemize}
\item The changes we made to our application for this task introduced a lot of bugs. It was voiced in our meetings a desire for a better system for keeping track of these. Currently these were only being conveyed verbally as well as being commented on in the source code. Hopefully we can introduce such a system in the following iteration.
\item We had some minor git related issues - these were fixed in consultation with our git leader.
\end{itemize}


\noindent

\section*{Satisfactory aspects of the iteration:}
\begin{itemize}
\item Last time we had a problem in which we split up our back log in tasks that were too big. This made it hard to estimate how long they would take and how much work they would require, consequently leading to some members doing bigger tasks than others. This time we have more effectively and successfully split up our tasks into manageble pieces of work. This means that the workload has been better and more evenly distributed as well as less distressful.
\item Complimentary to our preceding remark we have also been better at using and updating our to-do document. 
\item We are still very satisfied with the commitment and enthusiasm of our team members and we deem our communication to be good. As far as we know, the environment fostered in our group meetings facilitate an open discussion and a place in which everyone is heard and can ask questions.  
\end{itemize}
\noindent
\section*{Moving forward:}
As we do not know what the next assignment is we cannot fully prepare for what is to come. We are optimistic in regards of the code that we have written being malleable enough to accomodate for new changes (like alternate rule sets).

\vspace{4 mm}
\noindent
Some of the group members have made trivial suggestions like implementing a cogwheel option, a pop-up menu whilst in the game. As a side note we can add that we chose not to look at Stockfish in this assignment.
\end{document}
