\documentclass{article}
\usepackage[utf8]{inputenc}
\title{Team Plan - Team NASA}
\date{}
\begin{document}
\maketitle
\section*{Roles and responsibilities}
For now, we've chosen the following roles in our team:
\newline Team leader: Jonas Triki
\newline Git repository leader: Jonas Mossin Wagle
\newline Tool leaders:
\newline * libGDX, Jonas Triki
\newline * LaTeX, Marianne
\newline * Eclipse, Stian
\newline * PPT, Sofia

\section*{Organizing Git repository}

We’re going to organize the git repo in two branches: One for development (dev) and one for production (master). Each folder in the respective branch is going to represent a section of the application as a whole. For instance, we have one folder for documents called “docs” and one folder called “summaries” to keep track of all the meeting minutes. We have agreed to keep commit messages simple and clean, describing what changes has been made.

During the project ramp-up we plan to use the “docs” folder to keep track of all the .pdf/.tex files. Tasks have been distributed over all the team members to make sure we don’t work on the same thing, and during the weekly meeting we discuss what we have done and if we need to make any changes.

For the next iterations of the programming project (obligatory compulsory 3-5.) we have agreed to take an agile approach as to how to organize the Git repo. We are planning on using libGDX and a separate folder for all the Java codes is naturally for instance.

\section*{Risk analysis}
What could go wrong?
\newline * Team members can “fall off”
\newline * Team members may be inconsistent with delegated work tasks
\newline * Internal conflicts
\newline * Imprecise time management
\newline * Bad planning

\section*{Addressing issues}
How should the team react if it goes wrong, and if so, how to reduce the effect it has on the project?
\newline * Addressing issues as soon as possible. Do not let things lie.
\newline * Make sure everyone is on the same line and that everyone does what they are supposed to do.
\newline * Things usually take more time than expected; don’t set unrealistic deadlines.

\end{document}